Online Balanced Graph Partitioning: Optimizations for Large Clusters

### 2020-05-01 paper/disc20clustering.tex
Remark on resource augmentation
Typos

\noindent
\textbf{Remark on resource augmentation.}
The majority of work on Online Balanced Partioning so far (todo: cite) focuses on the scenerio with resource augmentation.
We note that this lower bound provides insights into this scenario as well.
Consider an instance with $k$ divisible by $3$, and construct $3$ ground sets of size $k/3$ in each cluster.
Then, apply the construction from the lower bound for $k=3$, now treating these ground sets in the way we used individual nodes.
For the resource augmentation as large as $1+1/3-\epsilon$, no more than $3$ such ground sets fit in one cluster.
Therefore, the lower bound $\Omega(\ell)$ holds.

>>>>

\noindent
\textbf{Remark on resource augmentation.}
The majority of work on Online Balanced Partitioning so far (todo: cite) focuses on the scenario with resource augmentation.
We note that this lower bound provides insights into this scenario as well.
Consider an instance with $k$ divisible by $3$, and construct $3$ ground sets of size $k/3$ in each cluster.
Then, apply the construction from the lower bound for $k=3$, now treating these ground sets in the way we used individual nodes.
For the resource augmentation as large as $1+1/3-\epsilon$, no more than $3$ such ground sets fit in one cluster.
The cost of any algorithm (including \OPT) scales up by $k/3$, and the lower bound $\Omega(\ell)$ holds.

Finally, we note the possibility for improvement (a gap). The algorithm CREP~\cite{repartition-disc} requires $(2+\epsilon)$-augmentation to guarantee the competitive ratio independent of $\ell$.
